Title Goes Here

### 2019-03-30 analysis/paper/paper.Rmd
Update paper.Rmd
fix the problem of reorder for factor by adding ungroup()

ornaments_count_test <-
  ornaments_period %>% 
  filter(!is.na(`6-layers`),
         Categories != "Unknown Metal") %>% 
  mutate(Categories = as.factor(Categories)) %>% 
  mutate(Categories = fct_lump(Categories, 
                               n = 5)) %>% 
  group_by(Categories) %>%
  count() %>% 
  ungroup() %>% 
  mutate(Categories = fct_reorder(Categories, n))

@@

```{r plot-counts-by-period}
# categories of ornaments by period
ornaments_count <-
  ornaments_period %>% 
  filter(!is.na(`6-layers`),
         Categories != "Unknown Metal") %>% 
  mutate(Categories = fct_lump(Categories, 
                               n = 5)) %>% 
  mutate(Categories = fct_infreq(Categories)) %>% 
  mutate(Categories = fct_rev(Categories)) %>% 
  group_by(period, Categories) %>%
  count() %>% 
  ungroup()

@@

```{r plot-count-type-by-period}
# plot for different shape of agate bead by period
agate_bead_shape <-
  ornaments_period %>% 
  filter(Categories == 'Agate bead') %>% 
  mutate(Type = ifelse(Type == 'prism/octagonal', 
                       str_remove(Type, '/octagonal'), Type)) %>% 
  mutate(Type = ifelse(Type == 'prism/pentagonal', 
                       str_remove(Type, '/pentagonal'), Type)) %>% 
  mutate(Type = ifelse(Type == 'prism/hexagonal', 
                       str_remove(Type, 'prism/'), Type)) %>% 
  mutate(Type = fct_infreq(Type)) %>% 
  mutate(Type = fct_rev(Type)) %>% 
  group_by(period, Type) %>% 
  count()

@@

# plot for different shape of metal bell by period
bell_shape <-
  ornaments_period %>% 
  filter(Categories == 'Bell',
         Type != 'unclassified') %>% 
  mutate(Type = fct_infreq(Type)) %>% 
  mutate(Type = fct_rev(Type)) %>% 
  group_by(period, Type) %>% 
  count()

@@

# plot for different shape of metal ring by period
ring_shape <-
  ornaments_period %>% 
  filter(Categories == 'Metal ring') %>% 
  mutate(Type = fct_infreq(Type)) %>% 
  mutate(Type = fct_rev(Type)) %>% 
  group_by(period, Type) %>% 
  count()

>>>>

ornaments_count_test <-
  ornaments_period %>% 
  filter(!is.na(`6-layers`),
         Categories != "Unknown Metal") %>%
  ungroup() %>% # need to upgroup because of rowwise or factor in previous chunk?
  mutate(Categories = fct_lump(Categories, 
                               n = 5)) %>% 
  group_by(Categories) %>%
  count() %>% 
  ungroup() %>% 
  mutate(Categories = fct_reorder(Categories, n))

@@

```{r plot-counts-by-period}
# categories of ornaments by period
ornaments_count <-
  ornaments_period %>% 
  filter(!is.na(`6-layers`),
         Categories != "Unknown Metal") %>%
  ungroup() %>% 
  mutate(Categories = fct_lump(Categories, 
                               n = 5)) %>% 
  mutate(Categories = fct_infreq(Categories)) %>% 
  mutate(Categories = fct_rev(Categories)) %>% 
  group_by(period, Categories) %>%
  count()

@@

```{r plot-count-type-by-period}
# plot for different shape of agate bead by period
agate_bead_shape <-
  ornaments_period %>% 
  filter(Categories == 'Agate bead') %>%
  ungroup() %>% 
  mutate(Type = ifelse(Type == 'prism/octagonal', 
                       str_remove(Type, '/octagonal'), Type)) %>% 
  mutate(Type = ifelse(Type == 'prism/pentagonal', 
                       str_remove(Type, '/pentagonal'), Type)) %>% 
  mutate(Type = ifelse(Type == 'prism/hexagonal', 
                       str_remove(Type, 'prism/'), Type)) %>%
  mutate(Type = fct_infreq(Type)) %>%
  mutate(Type = fct_rev(Type)) %>% 
  group_by(period, Type) %>% 
  count()

@@

# plot for different shape of metal bell by period
bell_shape <-
  ornaments_period %>% 
  filter(Categories == 'Bell',
         Type != 'unclassified') %>% 
  ungroup() %>% 
  mutate(Type = fct_rev(Type)) %>% 
  group_by(period, Type) %>% 
  count()

@@

# plot for different shape of metal ring by period
ring_shape <-
  ornaments_period %>% 
  filter(Categories == 'Metal ring') %>%
  ungroup() %>% 
  mutate(Type = fct_infreq(Type)) %>%
  mutate(Type = fct_rev(Type)) %>% 
  group_by(period, Type) %>% 
  count()
